Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-06-24 pirouette_article.tex
Process response letter

\new{
  % 00002
  In this paper, we focus on BD models, instead of coalescent models,
  although these are just as important. Coalescent models ... 
  [RJCB: Describe coalescent models]
}

@@

For example, one can add novel diversification models 
by writing a BEAST2 package that contains the likelihood 
formula of a phylogeny under the novel diversification model, 
i.e. the prior probability of a species tree.
Many diversification models (and their associated probability algorithms) 
have been developed, e.g., models in which diversification is time-dependent [\cite{nee1994reconstructed,rabosky2008explosive}],
or diversity-dependent [\cite{etienne2012diversity}],
or where diversification rates change for specific lineages 
and their descendants [\cite{etienne2012conceptual, rabosky2014automatic, alfaro2009nine}].
Other models treat speciation as a process that takes 
time [\cite{rosindell2010protracted, etienne2012prolonging, lambert2015reconstructed}],
or where diversification rate
depends on one or more traits [\cite{maddison2007estimating, fitzjohn2012diversitree}].
Despite such a rich theoretical landscape, only a few of these 
diversification models are available as tree priors in BEAST2
% 00005
\new{
  Despite the fact that some models are already included as tree priors 
  in BEAST2 (e.g. birth-death models, coalescent models, coalescent skyline, etc.) 
  many others for which a likelihood formula is already available 
  in literature, are not implemented yet.
}
\new{
  BEAST2 allows to extend its functionality by plug-ins, such
  as BD skyline (ref) [RJCB: name some other plug-ins with 
  refs to literature].
}

>>>>

\new{
  % 00002
  In this paper, we focus on BD models, instead of coalescent models,
  although these are just as important.
}

@@

For example, one can add novel diversification models 
by writing a BEAST2 package that contains the likelihood 
formula of a phylogeny under the novel diversification model, 
i.e. the prior probability of a species tree.
Many diversification models (and their associated probability algorithms) 
have been developed, e.g., models in which diversification is time-dependent [\cite{nee1994reconstructed,rabosky2008explosive}],
or diversity-dependent [\cite{etienne2012diversity}],
or where diversification rates change for specific lineages 
and their descendants [\cite{etienne2012conceptual, rabosky2014automatic, alfaro2009nine}].
Other models treat speciation as a process that takes 
time [\cite{rosindell2010protracted, etienne2012prolonging, lambert2015reconstructed}],
or where diversification rate
depends on one or more traits [\cite{maddison2007estimating, fitzjohn2012diversitree}].
Despite such a rich theoretical landscape, only a few of these 
diversification models are available as tree priors in BEAST2
% 00005
\new{
  Despite the fact that some models are already included as tree priors 
  in BEAST2 (e.g. birth-death models, coalescent models, coalescent skyline, etc.) 
  many others for which a likelihood formula is already available 
  in literature, are not implemented yet.
}
% 00014
\new{
  BEAST2 allows to extend its functionality by plug-ins, such
  as the calibrated Yule model (\cite{heled2015calibrated}),
  BD with incomplete sampling (\cite{stadler2009incomplete}),
  BD serial sampling (\cite{stadler2012estimating}),
  BD serial skyline (\cite{stadler2013birth})
  Fossilized BD process (\cite{gavryushkina2014bayesian}),
  BD SIR (\cite{kuhnert2014simultaneous}) and many more.
}
